Object Oriented Shader Composition Using CLOS

### 2018-02-21 els2018-glsl-oop/paper.tex
Forgot to link to glsl-toolkit.

void main(){
  color *= objectcolor;
}")
\end{minted}
\caption{A \code{colored-entity} class that encompasses vertex colouring functionality.}
\label{lst:colored-entity}
\end{listing}

@@

\section{Implementation}\label{section:8}
An implementation of the proposed system can be found at \href{https://github.com/Shirakumo/trial/blob/e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp}{https://github.com/Shirakumo/trial/blob/\\e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp}. A more in-depth discussion can be found at \\\url{https://reader.tymoon.eu/article/362}.

>>>>

void main(){
  color *= objectcolor;
}")
\end{minted}
\caption{A \code{colored-entity} class that encompasses object colouring functionality.}
\label{lst:colored-entity}
\end{listing}

@@

\section{Implementation}\label{section:8}
An implementation of the proposed system can be found at \href{https://github.com/Shirakumo/trial/blob/e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp}{https://github.com/Shirakumo/trial/blob/\\e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp} for the CLOS part, and at \url{https://github.com/Shirakumo/glsl-toolkit} for the merger part. \\

A more in-depth discussion of the system can be found at \\\url{https://reader.tymoon.eu/article/362}.
